Grupo Bimbo Inventory Demand \\Data Science Report

### 2024-07-15 src/data-science-project/data_science_project/docs/report/report.tex
Documents 95 percent
Docs 96 percent
Conclusion Documents

\section{Model Evaluation}
Model performance was evaluated using root mean squared error (RMSE) as the primary metric. Additional metrics such as precision, recall, and F1-score were computed to provide a comprehensive evaluation.
\begin{itemize}
    \item XGBoost Performance: The XGBoost model achieved an RMSE of X, demonstrating its superior predictive accuracy.
    \item Random Forest Performance: The Random Forest model had an RMSE of Y, indicating its relative performance compared to XGBoost.
\end{itemize}

@@

    \begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.9\textwidth]{images/quest1.png}
        \caption{Business Question 1}
        \end{center}
    \end{figure}

@@

    \begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.9\textwidth]{images/quest2.png}
        \caption{Business Question 2}
        \end{center}
    \end{figure}

@@

    % \begin{figure}[H] 
    %     \begin{center}
    %     \centering
    %     \includegraphics[width=0.9\textwidth]{images/quest2.png}
    %     \caption{Business Question 3}
    %     \end{center}
    % \end{figure}

@@

    \begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.9\textwidth]{images/quest4.png}
        \caption{Business Question 3}
        \end{center}
    \end{figure}

@@

\section{Conclusions}
This study demonstrates the effectiveness of machine learning models in forecasting product demand for Grupo Bimbo. The XGBoost model outperformed the Random Forest model, offering more accurate predictions. Integrating external economic indicators enhanced the model's accuracy. These findings can help improve inventory management, reduce waste, and optimize resource allocation. Future work could explore additional features and real-time model implementation for continuous insights.

\end{document}

>>>>

\section{Model Evaluation}
Model performance was evaluated using root mean squared error (RMSE) as the primary metric. Additional metrics such as precision, recall, and F1-score were computed to provide a comprehensive evaluation.
\begin{itemize}
    \item XGBoost Performance:

    \begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.8\textwidth]{images/comparisonxg.jpg}
        \caption{Heatmap correlation of the features}
        \end{center}
    \end{figure}

    \item Random Forest Performance:

    \begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.8\textwidth]{images/comparison.jpg}
        \caption{Actual vs Predict Adjusted Demand}
        \end{center}
    \end{figure}

@@

    \begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.8\textwidth]{images/quest1.png}
        \caption{Business Question 1}
        \end{center}
    \end{figure}

@@

    \begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.8\textwidth]{images/quest2.png}
        \caption{Business Question 2}
        \end{center}
    \end{figure}

@@

    % \begin{figure}[H] 
    %     \begin{center}
    %     \centering
    %     \includegraphics[width=0.7\textwidth]{images/quest2.png}
    %     \caption{Business Question 3}
    %     \end{center}
    % \end{figure}

@@

    \begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.8\textwidth]{images/quest4.png}
        \caption{Business Question 3}
        \end{center}
    \end{figure}

@@

\section{Conclusions}
This report demonstrates the application of machine learning models in forecasting product demand for Grupo Bimbo. The Random Forest model outperformed the XGBoost model, providing more accurate predictions of adjusted demand. The integration of external economic indicators, such as bi-weekly inflation rates and the consumer confidence index, significantly enhanced the model's accuracy. These findings highlight the potential of using advanced machine learning techniques to improve inventory management, reduce waste, and optimize resource allocation for Grupo Bimbo. Future work could involve incorporating additional features, such as macroeconomic indicators and weather data, to further enhance prediction accuracy.
\end{document}
